### 2020-12-13 README.Rmd
add Maoz global/regional power data.

- `capitals`: a list of capitals and capital transition for Correlates of War state system members
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)

>>>>

- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `maoz_powers`: Zeev Maoz' global/regional power data.
